From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-14 Pi+/paper/finite.tex

We state and prove two desirable properties of this relation on $\List[\Fin[n]]$ from the point of view of an abstract
rewriting system. We follow the terminology of~\cite{krausCoherenceWellFoundednessTaming2020}.
\vc{Not completely formalised.}

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item $\cox$ is (locally) confluent. For every span $w_{1} \cox w \cox w_{2}$, there is a matching extended cospan
          $w_{1} \cox* v \cox* w_{2}$.
    \item $\cox*$ is strongly normalising. For every $w$, there exists a unique $v$ such that $w \cox* v$. Equivalently,
          the type $\dsum{v:\List[\Fin[n]]}{w \cox* v}$ is contractible, and $w \cox* v$ is a proposition for every $w$
          and $v$.
  \end{enumerate}
\end{proposition}

@@

>>>>

\todo{Long form of Coxeter relations and their equivalence.}

We state and prove two desirable properties of this relation on $\List[\Fin[n]]$ from the point of view of an abstract
rewriting system. We follow the terminology of~\cite{krausCoherenceWellFoundednessTaming2020}. \vc{Not completely
  formalised. Is this with Coxeter or LongCoxeter?}

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item $\cox$ is (locally) confluent. For every span $w_{1} \cox w \cox w_{2}$, there is a matching extended cospan
          $w_{1} \cox* v \cox* w_{2}$.
    \item $\cox*$ is strongly normalising. For every $w$, there exists a unique $v$ such that $w \cox* v$.
          \review{Equivalently, the type $\dsum{v:\List[\Fin[n]]}{w \cox* v}$ is contractible, and $w \cox* v$ is a
          proposition for every $w$ and $v$.}
  \end{enumerate}
\end{proposition}

@@

We will now prove the group structure of $\Sn$.
